A large-scale analysis of racial disparities in police stops across the United

### 2020-02-28 lib/paper_results.Rmd
fixing plot filenames

Scaling priors by 0.5x:
```{r disparity-thresholds-tables-0.5}
kable(disp$city$threshold$prior_scaling_factor_0.5$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_0.5$results$aggregate_thresholds)
```

Priors at 1.0 (normal):
```{r disparity-thresholds-tables-1.0}
kable(disp$city$threshold$prior_scaling_factor_1$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_1$results$aggregate_thresholds)
```

Scaling priors by 1.5x:
```{r disparity-thresholds-tables-1.5}
kable(disp$city$threshold$prior_scaling_factor_1.5$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_1.5$results$aggregate_thresholds)
```

@@

```{r mj_inferred_threshold_plot_0.5_prior_scale, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes$prior_scaling_factor_0.5$plot
```

@@

```{r mj_inferred_threshold_plot_1.5_prior_scale, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes$prior_scaling_factor_1.5$plot
```

>>>>

Scaling priors by 0.5x:
```{r disparity-thresholds-tables-0_5}
kable(disp$city$threshold$prior_scaling_factor_0.5$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_0.5$results$aggregate_thresholds)
```

Priors at 1.0 (normal):
```{r disparity-thresholds-tables-1_0}
kable(disp$city$threshold$prior_scaling_factor_1$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_1$results$aggregate_thresholds)
```

Scaling priors by 1.5x:
```{r disparity-thresholds-tables-1_5}
kable(disp$city$threshold$prior_scaling_factor_1.5$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_1.5$results$aggregate_thresholds)
```

@@

```{r mj_inferred_threshold_plot_0_5_prior_scale, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes$prior_scaling_factor_0.5$plot
```

@@

```{r mj_inferred_threshold_plot_1_5_prior_scale, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes$prior_scaling_factor_1.5$plot
```
